Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
added names for Cmaj->Fmaj chord transition

The 25 most frequently used codewords in the test set are shown in
Figure \ref{fig:codes1}.  
The frequency of use of these codewords are shown in Figure \ref{fig:freqs}.
The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 0),
perfect fifth (codewords 1 and 2) and fourth intervals (codewords 3
and 6), and a
major and minor triads (codewords 5 and 4, respectively).  Many of the remaining
codewords correspond to common transitions from one chord to another,
\eg a transitions between major triads in codes 7 and 9 ( Cmaj
$\rightarrow$ Fmaj or C5 $\rightarrow$ F5 as a guitar power chord)
% assuming that chroma 0 is C) 
and the reverse transition in code 21 (\ie Fmaj $\rightarrow$ Cmaj).
%FIXME: Does this transition have a better name like ``relative x''?
% C5 -> F5 in 'guitar chords', basically a power chord

\begin{figure}[h]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most frequently used codes in the codebook %in term of frequency of use
in the artist20 test set. 
This codebook contains $200$ codes trained on $2$ bar, $12 \times 8$
patches.
The numbers 
%above each panel correspond to the display are the index (from most used to least) and
in parentheses correspond to 
the percentage of use in the test set.
%There are $71832$ patterns in total in the dataset.
}}
\label{fig:codes1}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{codes_8bars}
\end{center}
\caption{\small{Sample of longer codewords spanning over $8$ bars. Codewords
selected randomly from the codewords used in the test set. Percentage of
used display in parentheses.
Most patterns are sustained notes, but codeword 0 shows a repeted two notes
pattern.
}}
\label{fig:codes8bars}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{song_encoded}
\end{center}
\caption{\small{Good Day Sunshine by \textit{The Beatles}.
Original song and its encoding using a $200$ codes codebook learning
$2$ bars at a time.
}}
\label{fig:encodesong}
\end{figure}

>>>>

The 25 most frequently used codewords in the test set are shown in
Figure \ref{fig:codes1}.  
The frequency of use of these codewords are shown in Figure \ref{fig:freqs}.
The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 0),
perfect fifth (codewords 1 and 2) and fourth intervals (codewords 3
and 6), and a
major and minor triads (codewords 5 and 4, respectively).  Many of the remaining
codewords correspond to common transitions from one chord to another,
\eg a tonic-subdominant transition in codes 7 and 9
(Cmaj
$\rightarrow$ Fmaj or C5 $\rightarrow$ F5 as a guitar power chord)
% assuming that chroma 0 is C) 
and the reverse tonic-dominant transition in code 21 (\ie Fmaj
$\rightarrow$ Cmaj).
%FIXME: Does this transition have a better name like ``relative x''?
% C5 -> F5 in 'guitar chords', basically a power chord

\begin{figure}[h]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
25 most frequently used codes in the codebook %in term of frequency of use
in the artist20 test set. 
This codebook contains $200$ codes trained on $2$ bar, $12 \times 8$
patches.
The numbers 
%above each panel correspond to the display are the index (from most used to least) and
in parentheses correspond to 
the percentage of use in the test set.
%There are $71832$ patterns in total in the dataset.
}}
\label{fig:codes1}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{codes_8bars}
\end{center}
\caption{\small{Sample of longer codewords spanning over $8$ bars. Codewords
selected randomly from the codewords used in the test set. Percentage of
use display in parentheses.
Most patterns are sustained notes, but code 0 shows a repeating two chord
pattern.
}}
\label{fig:codes8bars}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{song_encoded}
\end{center}
\caption{\small{Good Day Sunshine by \textit{The Beatles}.
Original song and its encoding using a $200$ entry codebook learning
$2$ bars at a time.
}}
\label{fig:encodesong}
\end{figure}
